%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Luyanda}{Mncube}{ \urlstyle{same}\href{https://luyandamncube.github.io/}{luyandamncube.github.io} \href{github.com/luyandamncube}\\
\href{mailto:luyanda.mncube@outlook.com}{luyanda.mncube@outlook.com} | 061 116 7195 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{UNISA - Ongoing}
\descript{Bsc CompSci \& Mathematics}
\location{Expected grad. 2027 | JHB}
\sectionsep

\subsection{Wethinkcode}
\location{2018 | JHB}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certification}
% \subsection{Undergraduate}
MCSA: Database Development \\
DP-203: Azure Data Engineer Associate
Certified SAFe \textregistered Agilist \\
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\subsection{AI-Driven Notifications}
Thames Water and Sand Technologies

A DS/DE feature that identifies bursts within a digital twin of a water network.

\sectionsep

\subsection{Digital Water Balance}
A set of DE features to account for all water movement through a defined volume in various areas including S/N London, S/N Oxford, Guildford \& SWA.

\sectionsep

% {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\s
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
% \subsection{Undergraduate}
Water Industry Awards UK - Nomination\\
Smart Water Networks award \\
\textbullet{} AI-Driven Notifications \\
\sectionsep

Architected Data Warehouse Solution \\
\textbullet{} Successfully implemented Azure-based warehousing solution, for daily PostgreSQL data backup.
\sectionsep

Architected Bronze/Silver data ingestion \\ 
\textbullet{} Successfully implemented Azure-based data ingestion of various complex data sources, including telemetry data, \& Geospatial data. Data used to estimate daily water leakage.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\vspace{\topsep}
\begin{tightemize}
\item Enterprise Data Architecture Design
\item Dimensional Modeling
\item Data Warehouse Schema Development
\item Performance Optimization and Query Tuning
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PERSONAL SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Summary}

Senior Data Engineer with 6+ years of experience delivering modern data platforms in fast-paced, client-facing environments. Proven expertise in building scalable ETL/ELT pipelines, orchestrating distributed workloads (Spark/Databricks), and deploying cloud-native data infrastructure across Azure and AWS. Comfortable working across engineering and business teams to drive reliable, secure, and observable data systems at scale.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{LexisNexis}
\descript{| Data Engineer (Platform \& Architecture) }
\location{Sep. 2025 - Present | JHB (Remote)}
\vspace{\topsep}
\begin{tightemize}

\item Platform/data architecture work, designing reliable ingestion and serving patterns for production analytics systems.

\item Provisioned and operated Elasticsearch indexing workflows and MSK (Kafka) infrastructure, improving scalability and operational consistency across environments.

\end{tightemize}
Tech Stack: AWS (MSK, Step Functions, Lambda, S3, RDS), Elasticsearch, Terraform, Docker, PostgreSQL/SQL Server, Python, SQL
\sectionsep


\runsubsection{Sand Technologies (prev. EXPLORE AI)}
\descript{| Data Engineer }
\location{Oct. 2021 - Present | JHB (Remote)}
\vspace{\topsep}
\begin{tightemize}
\item Built scalable ingestion and transformation pipelines across Azure Data Factory and Databricks (Spark) for telemetry and geospatial data.
\item Designed data models supporting a unified digital water balance framework across multiple source systems.
\item Delivered production data products end-to-end with CI/CD via Azure DevOps.
\end{tightemize}
Tech Stack: Azure Data Factory, Databricks, Spark, MSSQL, PostgreSQL, Python
\sectionsep

\runsubsection{Yebofresh}
\descript{| Software Engineer }
\location{Mar. 2021 - Oct. 2021 | Airport Industria, CPT (Remote)}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Improved core data models \& features of mobile e-commerce apps.
\end{tightemize}
\sectionsep

\runsubsection{NTT (prev. Dimension Data)}
\descript{| Data Engineer }
\location{Feb. 2019 - Mar. 2021 | Bryanston, JHB}
\vspace{\topsep}
\begin{tightemize}
\item Built and maintained batch + streaming pipelines for live telemetry and editorial datasets used across TV, mobile, and web.
\item Developed core data models (asset hierarchies, metadata) enabling analytics and visualization.
\item Provided live race-day support for global events (e.g., Tour de France, Zwift/UCI esports).
\end{tightemize}
Tech Stack: MSSQL, Python, Apache NiFi, Apache Beam, Docker, Bash
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Key Skills \& Compentencies} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
% \begin{tightemize}
% \item Experience in Developing Spark applications using Spark
% \item Good understanding of Big Data Hadoop with specialization in streaming data 
% \item Experience in Database Design and development using SQL Server \&  pgAdmin
% \item Excellent communication skills, including the ability to convey analytics insights effectively to both IT and business audiences.
% \item Expertise in various phases of project life cycles (Design, Analysis, Implementation and testing).

% \end{tightemize}
\begin{tabular}{ l l }
% Cloud Platforms: & Azure (Data Factory, Data Lake, Databricks, DevOps), AWS (basic) \\
% Languages: & Python, SQL, C\#, Shellt \\
% Data Tools: & Spark, Kafka, NiFi \\
% Databases: & SQL Server, PostgreSQL, MySQL \\
% DevOps: & Azure Pipelines, Docker, Git, CI/CD \\
% Frameworks: & ReactJS \\
% Methodologies: & Agile, Scrum, Domain-Driven Design \\

Data Modeling: & Microsoft SQL Server, dbdiagram.io, Luna Modeler \\
Databases: & MySQL, Microsoft SQL Server, PostgreSQL \\
Data Warehousing: & Databricks, Azure Datalake \\
Programming: & Python (Pandas, NumPy), SQL, Shell \\
DevOps: & Azure Pipelines, Docker, Terraform, Git \\
Data Streaming: & Spark, Kafka, NiFi \\


\end{tabular}
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
